---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OrderedHeatMapAnalysis

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

Optimised direct visualization and analysis of matrix data structure.

## Installation

You can install the development version of OrderedHeatMapAnalysis from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("NoeDemange/OrderedHeatMapAnalysis")
```

## Example

This is a basic example which shows you how to run the app:

```{r example}
library("OrderedHeatMapAnalysis")
OrderedHeatMapAnalysis::run_app(options=list("launch.browser"=TRUE))
```

## Credits

This app was developed by [Noe Demange](https://github.com/NoeDemange).
It was developed for and is maintained by [Guillaume Sapriel](https://orcid.org/0000-0003-0549-9376).
It is deployed on the [MIGALE platform](https://migale.inrae.fr/) by [Cédric Midoux](https://orcid.org/0000-0002-7964-0929). We are grateful to the INRAE MIGALE bioinformatics facility (MIGALE, INRAE, 2020. Migale bioinformatics Facility, doi: 10.15454/1.5572390655343293E12) for providing help and storage resources.

